---
title: "yunhuaz_Homework2"
format: html
editor: visual
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

What is the probability that she will hear more than 8 calls during any given sessions?

```{r}
#Mean number of calls
l <- 15

#Probability its greater than 8
p_greater_than_8 <- 1 - dpois(8, lambda = l) 

p_greater_than_8
```

What is the probability that she will hear no calls in a session?

```{r}
#Mean number of calls
l <- 15

#Probability of no calls
p_no_calls <- dpois(0, lambda = l)

p_no_calls
```

What is the probability she will hear exactly 3 calls in a session?

```{r}
#Mean number of calls
l <- 15

#Probabiltiy of exactly 3 calls
p_3_calls <- dpois(3, lambda = l)

p_3_calls
```

Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
x <- 0:30
l <- 15

probset <- dpois(x = x, lambda = l)

barplot(probset, names.arg = x, space = 0, xlab = "x", ylab = "Pr(x = x", main = "Probablity Mass Function")
```

Simulate 104 results from this distribution (i.e., 2 years of Saturday morning sessions. Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
set.seed(1)
sim_results <- rpois(n = 104, lambda = 15)

hist(sim_results, breaks = 15, xlab = "Number of Calls", ylab = "Frequency", main = "Histogram of Simulated Poisson Results", xlim = c(0,30))
```

Specifying a seed when generating a random sample allows for the same "random" sample every time we run that cell. This ensures reproducibility in this code, I specified the seed to be one ensure that I receive the same sample of size 104 from a Poisson(15) distribution.

The histogram I plotted for the simulated results displayed a bimodal shaped distribution, the probability mass function displayed a normal distribution. Overall, based on the tails if we were to generate more samples we are able to create a similar shape to the probability mass function.
