---
title: "yunhuaz_Homework2"
format: html
editor: visual
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

> BP: Gonna echoe Christian's comments regarding formatting and the use of Rmd instead of Qmd to make sure your the theme works properly.

What is the probability that she will hear more than 8 calls during any given sessions?

```{r}
#Mean number of calls
l <- 15

#Probability its greater than 8
p_greater_than_8 <- 1 - dpois(8, lambda = l) 

p_greater_than_8
```

> BP: I might be wrong, but I think dpois only returns the probability of that exact value within the distribution (i.e. P(X = x)), so 1- dpois(8, 15) like you have here would be returning the probability of *any* value other than 8 rather than just those above 8. I think you need the cumulative probability function ppois for this instead. I just set the lower.tail = FALSE to make sure I was grabbing all the probabilities of numbers above 8.

What is the probability that she will hear no calls in a session?

```{r}
#Mean number of calls
l <- 15

#Probability of no calls
p_no_calls <- dpois(0, lambda = l)

p_no_calls
```

> BP: Looks good! Though I think it'd be a good idea to comment your code a bit more just to make it easier to follow along with what you're doing.

What is the probability she will hear exactly 3 calls in a session?

```{r}
#Mean number of calls
l <- 15

#Probabiltiy of exactly 3 calls
p_3_calls <- dpois(3, lambda = l)

p_3_calls
```

Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
x <- 0:30
l <- 15

probset <- dpois(x = x, lambda = l)

barplot(probset, names.arg = x, space = 0, xlab = "x", ylab = "Pr(X = x)", main = "Probablity Mass Function")
```

> BP: Not sure what's happening but I'm getting an error saying "Error in (function (filename = "Rplot%03d.png", width=480, height=480,: unable to start png() device"
>
> Not entirely sure what to make of that, but it might have something to do with the file path that I'm using for this cloned repo. Either way probably a good thing to check.

Simulate 104 results from this distribution (i.e., 2 years of Saturday morning sessions. Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
set.seed(1)
sim_results <- rpois(n = 104, lambda = 15)

hist(sim_results, breaks = 15, xlab = "Number of Calls", ylab = "Frequency", main = "Histogram of Simulated Poisson Results", xlim = c(0,30))
```

Specifying a seed when generating a random sample allows for the same "random" sample every time we run that cell. This ensures reproducibility in this code, I specified the seed to be one ensure that I receive the same sample of size 104 from a Poisson(15) distribution.

The histogram I plotted for the simulated results displayed a bimodal shaped distribution, the probability mass function displayed a normal distribution. Overall, based on the tails if we were to generate more samples we are able to create a similar shape to the probability mass function.

> BP: I like that you specify a seed for the random sample to ensure it's consistent across different times running the code chunk, that's something I should try to utilize in my own code for this problem. Interesting that your results ended up displaying a bimodal distribution, mine definitely had multiple discrete local peaks across the distribution but I'm not sure that I could call it truly bimodal, since the peaks and valleys I saw looked more like noise rather than a true representation of the distribution. (also for clarity's sake I'm not sure I'd describe the graph of the probability mass function as following a "normal" distribution since it's explicitly a poisson distribution and therefore not, strictly speaking, continuous, but that might just be a nitpick.)
>
> Great work! Just think you might want to consider commenting your code a bit more to make things a bit clearer.
